---
title: "Analysis of return correlation between traditional and crypto assets "
author: "Luca Laboranti, Giancarlo Meccariello"
date: "18. Mai 2022"
output:
  pdf_document: default
  html_document: default
  bibliography: references.bib 
---
\newpage
\tableofcontents
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

In Harry Markowitz’s words “diversification is the only free lunch in investing”. With global stocks and bonds experiencing a severe downturn in Q1 2022 mainly due to a combination of rising inflation, the Ukraine conflict, and fresh lockdowns in China, achieving high diversification within the traditional asset classes for many investors is not enough to avoid steep losses. Investors have therefore looked at alternative asset classes to drive diversification in their portfolio. Most notably, crypto assets have been on investors’ radar for many years and their effect on diversification has been a topic of extensive research.
This paper aims at providing additional perspective on the diversification effects of crypto assets when added to a portfolio of traditional assets classes by analyzing the historical return correlation between the two and zeroing in on their relationship during market up and downswings. 
This paper features (data analysis techniques employed in the research)

# Literature Review

One of the earliest papers to analyze the return correlation of a crypto asset with traditional and other alternative investment classes was Brière et al. in 2015. The paper concluded that  over the period under consideration, Bitcoin (the only crypto asset analyzed in the paper) had exceptionally high average return2 and volatility and its correlation with other assets was remarkably low. Spanning tests conducted in the paper confirmed that BTC investment offers significant diversification benefits and its addition to a well-diversified portfolio may improve the risk-return trade-off.
In light of the covid pandemic and the connected dramatic market sell-off this topic has been revisited in multiple papers e.g. Allen (2022); Massoumi and Wu (2021); Kristoufek (2020); Conlon et al. (2020); Lahmiri and Bekiros (2020); Grobys (2021). The result from these studies was a resounding contradiction to Brière et al. paper. In fact, they showed that the main cryptocurrencies did not provide a strong portfolio diversification tool in the context of the covid crisis.


# Selection of benchmarks


We selected a basket of investment objects to represent a traditional investment porfolio.

* Stocks and bonds:
    + S&P500
    + AGG


* Crypto currencies:
    + Bitcoin
    + Etherium
    


# Historical return correlation between traditional and crypto assets

In following we represented the weekly historical returns from 2017 to 2022 of the investment instruments listed above, and the two crypto assets analyzed.

## Decomposition

## Augmented-Fuller Test

# Return correlation between traditional and crypto assets

The following table shows the correlation matrix between the assets analyzed throughout the period considered above (from 2017 to 2022). Here we highlighted the correlation of crypto assets with traditional assets.

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
a <- 1
```

We are going to use the `e1071` package for this example and also some helper functions from `caret`

Correlation   | S&P500        | EGG         | Bitcoin     | Etherium
------------- | ------------- |-------------|-------------|-------------
S&P500        | `r a`         |               |           |
EGG           |               | `r a`          |               |
Bitcoin       |               |           |       `r a`         |
Etherium      |               |           |               | `r a` 

